\huge A Usability Evaluation of Tor Launcher

### 2016-11-11 pets2017-paper/pets2017-paper.tex
\chi^2 rather than X^2.
add formative demographics

Bridges are unlisted Tor relays that serve as an alternative entry node.
Bridges can be unlisted relays that behave similarly to a regular Tor relay,  
but most run a pluggable transport (referred to as ``transport'' for shorthand) that obfuscates traffic. 
Most transports rely on the secrecy of their static IP addresses for their effectiveness.
These include ``fte'' and ``fte-ipv6''~\cite{fte},
which disguise the Tor protocol as another protocol (such as HTTP), and
``obfs3''~\cite{obfs3}, ``obfs4''~\cite{obfs4}, and ``scramblesuit''~\cite{scramblesuit},
which encrypt or alter the Tor protocol to appear as random noise.
Other transports route traffic through other services and do not need secret IP address. 
``flashproxy''~\cite{flashproxy} connects through third party web browsers,
and the ``meek''~\cite{fifield2015blocking} options route traffic
through content delivery networks. Fig.~\ref{fig:bridge-options} shows the bridge and transport options at the time of the study.

@@

\subsection{State and Corporate Censorship}
State level censors block access to the Tor network by blocking Tor relays, which are publicly listed. Some also employ more sophisticated techniques such as deep packet inspection and protocol detection. This means that users can connect to the Internet, but not through Tor. The thoroughness of censorship is what requires different bridges and transports.

A local proxy is required to connect in certain managed networks (i.e. company and university firewalls). This usually means that users cannot connect to the Internet at all without a proxy, including connecting to the Internet through Tor. The user must be able to connect to the Internet through their proxy before trying to connect to the Internet with Tor.

@@

\subsection{Testing Pipeline} 
Two researchers first performed a cognitive walkthrough~\cite{cognitive-walkthrough} to prepare for user testing. A cognitive walkthrough is evaluation method that requires usability evaluators to work through a series of tasks from the perspective of the user, usually to understand a system's learnability for new or infrequent users.

@@

We concluded with a summative usability test~\cite{summative} that measured the usability of the current and redesigned interface. This testing is a usually used as quality assurance tool to test features. In short, formative testing tells you {\it what} is is not usable, while summative testing testing tells you {\it if} it is or is not usable. Twenty users is considered to be a minimum for statistically significant measurements~\cite{howmanyusers}, so we recruited twenty participants for each experimental condition.

@@

\begin{itemize}
\item {\bfseries Completion rate:}  percentage of users that connect to Tor in an experimental condition. 
\item {\bfseries Connection time:} time from Tor Browser startup to a successful connection to Tor. 
\item {\bfseries Configuration time:} time users spent in Tor Launcher configuring bridges and proxies.
\end{itemize}

@@

We simulated three environments of increasing severity in censorship (E1, E2, E3).
Table~\ref{tab:environments} summarizes them and explains what is required to connect to Tor. We chose to 
simulate environments for the stability and reproducibility of the 
experiment, as real censored networks are volatile and complex.

@@

\subsection{Procedure} 
Two researchers performed the cognitive walkthrough on the Tor Browser 5.0.3 Tor Launcher GUI, the most recent version deployed at the time (Figure~\ref{fig:old-interface}). We systematically tried action sequences from the perspective of a typical user, which we defined as a first time or infrequent user with almost no previous knowledge about network components involved in connecting to Tor.

@@

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{tor-digraph.png}
\caption{
A digraph illustrating the potential user paths through the interface. Non-leaf nodes are screens in the user interface (start, bridge 1, bridge 2, proxy 1, proxy 2, and progress). Leaf nodes are various end states (quit, success, or error). Transitions between these nodes denote user actions. For details of each end state, see Appendix ~\ref{states}. 
}
\label{fig:digraph}
\end{figure*}

@@

\subsection{Recruitment}
We recruited people from Craigslist using the recruitment text in Appendix~\ref{qualitative-recruitment}, which linked an prescreening survey that collected demographics (Appendix~\ref{qualitative-prescreening}). We pre-screened~\cite{screening} for diversity in gender, age, technical expertise, use of security tools, and familiarity with Tor in a small participant pool. {\color {red} Of our 16 recruited participants, 53.3\% were male. Ages ranged from 20 to~62 years ($\mu = 24.5$, $\sigma = 12.6$). 93.3\% of our participants had college education.} We took participants' self-reported familiarity with technical terms use of security tools with skepticism (Appendix~\ref{prescreening-responses}). We verified their self-reported familiarity with Tor Browser in-person, and found that 4 used it, 5 heard of it but not used it, and the remaining 8 never heard of or used it. The main objective of this question was to identify new users versus infrequent users. We considered participants who had never heard of Tor or have only heard of Tor to be new users and those who have used Tor to be previous users.

@@

After participants completed the browsing tasks (or ran out of time),
we asked them standard interview questions about their experience (Appendix~\ref{interview-questions}) and took notes of their responses. We then followed up with participant-specific questions to verify any hypotheses   we had from observation (e.g. ``the participant was selecting bridges at random''). We paid each participant~\$30 for their time.

\subsection{Results} 
We give a summary of what our participants did below. We watched the screen recording to summarize their actions and referred to their interviews for insight into why they took specific actions.

@@

In E2, a bridge was required to connect, but any bridge worked. Configuring a proxy was optional.
Participants in E2 {\it eventually} connected using the recommended bridge, but spent a fair bit of time waiting for direct connections to fail and unsuccessfully configuring proxies. 
Observations in E2:

@@

\subsection{Procedure} 
Three researchers agreed on security and usability design principles. 
We then rewatched screen capture videos and read interview transcriptions to brainstorm design changes. We provided the security and usability design principles, screen capture videos, interview transcriptions, and our suggested changes to a user interface designer, who iteratively redesigned the interface with our feedback and user interface best practices in mind. Figure~\ref{fig:new-interface} shows our redesign of the interface.

\begin{figure*}
\centering
\begin{subfigure}[b]{0.35\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-first.png}
	\caption{The first screen. We reduced the text on the screen and clarified that configuration is for heavily censored environments.}
	\label{fig:new-first}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.35\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-proxyYES.png}
	\caption{The interface detects the need for a proxy. Proxy fields (same as ones in Figure \ref{fig:old-proxy-yes} are hidden until you click``configure.''}
	\label{fig:new-proxy}
\end{subfigure}
\begin{subfigure}[b]{0.35\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeSettings.png}
	\caption{There is only one bridge screen now. The default is to connect without one.}
	\label{fig:new-nobridge}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.35\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeSettings-default.png}
	\caption{We give short instructions on when to use a bridge. Users can configure one here.}
	\label{fig:new-bridge}
\end{subfigure}
\begin{subfigure}[b]{0.35\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeSettings-combobox.png}
	\caption{The transports selections are the same.}
	\label{fig:new-bridge-combobox}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.35\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeHelp.png}
	\caption{These instructions are also the same.}
	\label{fig:new-bridge-help}
\end{subfigure}
\begin{subfigure}[b]{0.35\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-summary.png}
	\caption{This screen summarized how they would connect to Tor. There is more information if bridges and proxies are configured.}
	\label{fig:new-summary}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.35\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-progress.png}
	\caption{A checkpoint progress bar with connection information. There are more checkpoints if bridges and proxies are configured.}
	\label{fig:new-progress}
\end{subfigure}
\caption{
A redesigned version of the Tor Browser 5.0.3. Tor Launcher GUI. Screens are in the order that they appear. 
}
\label{fig:new-interface}
\end{figure*}

\subsection{Design Principles} 
The interface currently favors a guided manual configuration over an automated configuration with network probing. Our redesign preserves this approach and has no user-dependent inputs, no network-dependent inputs, and minimal information leaks.

@@

\subsection{Recruitment}
We recruited  people using the recruitment text in Appendix~\ref{quantitative-recruitment}. We recruited 65 participants from Craigslist and 59 participants from the <redacted lab> participant pool. <Redacted lab> encouraged the use of their participant pool, but we bargained to recruit participants from Craigslist to ensure a diverse set of participants. Although the <redacted lab>'s participant pool is not limited to students and staff from <redacted institution>, it was estimated that a large majority were.

{\color {red} Of our recruited 124 participants, 56.8\% were male. Ages ranged from 18 to~68 years ($\mu = 28.9$, $\sigma = 12$). 56.8\% were male. 84.8\% of our participants had a college education.} We distributed participants evenly across experimental condition, about 20 in each interface and environment combination. Although there is variation in gender and age in each experimental condition, we ensured each condition had about half Craigslist recruited participants and half <redacted lab>  pool participants.

@@

\subsection{Procedure}
Participants were assigned to a computer at random, which effectively assigned them to a simulated censorship environment combination at random. Before the experiment began, participants were verbally informed of the purpose of the study, what data was collected, and any associated risks. If they wished to participate, they were informed again in writing and consented by signing the document. To be thorough, we clarified that they could stop at any time during the experiment with no negative consequences.

The experiment formally began by informing participants of the simulated censorship environment, giving them their worksheet, and informing them that Tor browser is necessary to circumvent censorship (Appendix~\ref{quantitative-script}). This time, the worksheet only asks users to visit one blocked website (Wikipedia) and explicitly reminds users to use Tor to do so. Before participants started their tasks, we reminded them that their screens are being recorded so they should not log into anything that shows personal information. We gave users a chance to ask any questions about the experiment or task.

@@

%table
\begin{table}[t]
\centering
\input{attempts-bridge-proxy.tex}
\caption{
Network components that led to the first successful bootstrap
in each condition.
Most successful E1 participants used a direct connection,
but a few optionally used an obfs3 bridge.
All successful E2 participants used 
an obfs3 bridge (the recommended option)---none used 
flashproxy, fte, fte-ipv6, obfs4, or scramblesuit bridges to connect. 
Most successful E3 participants
used a meek bridges, disfavoring meek-azure.
One E3 participant succeeded in an unexpected way
by using an open proxy and configuring it to bypass our 
simulated environment.
}
\label{tab:attempts-bridge-proxy}
\end{table}

@@

% failure observations
17\% (19 of 114) of participants were not able to successfully connect to Tor. Five (P73, P75, P89, P91, P106, P110) tried a direct connection. When that failed, they assumed there was something wrong with their computer, network settings, or the Tor network and never tried to configure bridges or proxies. Five (P74, P92, P105, P107, P113) users who need a bridge assumed that they needed a proxy to connect to Tor. We believe this may be due to the fact that the OLD interface defaults to showing users the proxy page (because it is the one before the progress screen) when a connection fails. Five (P90, P93, P108, P111, P114) users who needed a meek or custom bridge tried the suggested bridge (obfs3), but didn't know what to do when that failed. Two (P94, P109) users who needed a meek or custom bridge tried to get custom bridges but failed to format their email content correctly to get a response from the bridges autoresponder. We suspect that they would have succeeded if they had gotten a response.

@@

\subsubsection{Connection time} 
Connection time is the time from Tor Browser startup to the first successful Tor bootstrap. Non-finishing participants are assigned the maximum experiment time of 40:08. Table~\ref{table:participant-summary} summarizes the median times while Figure~\ref{fig:time_to_success_clamped} shows their distribution. Figure~\ref{fig:time_to_success_ecdf} shows the cumulative success rates over time.

@@

\subsubsection{Configuration Time} 
Configuration time is the time spent configuring network components, which we define as the completion time minus any time spent on the progress screen. Table~\ref{table:participant-summary} shows the median times and Figure~\ref{fig:time_to_success_active_clamped} shows their distribution. Table~\ref{table:median_time} shows the percentage of time spent on each screen. Note that the time spent configuring bridges and proxies is {\it not} equivalent to the amount of time participants spent trying to connect, which would be the connection time minus the time spent on the progress screen for the last time (time Tor takes to bootstrap after a valid configuration).

%things to keep in mind
We believe that configuration time is a meaningful metric because 1) bootstrapping can take a couple minutes, which dominates measurements for users do not need much time to configure their connection, such as participants in E1. and 2) some mistakes, such as using a syntactically valid but unusable proxy, generate non-interrupting warnings and let the users wait indefinitely at until they manually cancel the connection to try again. But this is not the most accurate measurement of time spent configuring, since it does not reflect how some participants searched for help in another browser while waiting on the progress screen.

@@

\subsection{Usability of Tor Launcher} 
In total, 63\% (72 of 114) of first attempts to connect failed and 79\% (363 of 458) of total attempts to connect failed. 
On average, users who required a bridge took over 3 minutes to connect to Tor, and users who required a meek or custom bridge took over 20 minutes.

@@

Participants in a laboratory setting may alter their due to their awareness of being observed~\cite{mccarney2007hawthorne}. We are aware that our participants were likely motivated differently compared to real users. We believe that participants were likely overmotivated to connect to Tor because they were being observed and receiving a monetary reward. If true, this makes our results are a conservative estimate of the current usability problems.

@@

We only tested interface on Windows machines, which were the machines available at <redacted>. %Xlab.
The configuration interface leverages the native operating system's styling and elements, making the configuration interface on Windows look slightly different from the OS~X or Linux equivalent. Additionally, we acknowledge that participants' unfamiliarity with Windows may have affected our experiment, but we believe that this affected all experimental conditions minorly and equally.

@@

\section {Acknowledgments}
Many generous people helped us along the way. <Redacted> assisted with testing our setup and teardown scripts, offered recruitment services, and allowed us to run experiments after <redacted lab>'s hours. <Redacted> and <redacted> were instrumental during the design process, as they helped me iterate through many not-so-great ideas.  <Redacted>,and <redacted> provided me with insider insight into the design decisions made at Tor.
% Rowilma del Castillo. Nima Fatemi and Isabela Bagueros.  Georg Koppen and the Tor UX team.

@@

{\color {red}
\section{Prescreening Survey Responses}
\label{prescreening-responses}
We asked people how familiar they were with some technical terms and security tools during our prescreening survey for formative usability testing. We show the responses from the participants that we chose.

\begin{table}[h]
\centering
\begin{tabular}{l r r}
& Familiarity\\
\noalign{\hrule}
Malware & 00/00\\
Proxy services & 00/00\\
Phishing & 00/00\\
SSL & 00/00\\
X.511 certificates & 00/00\\
Tor & 00/00\\
\end{tabular}
\caption{
An overview of the results of the experiment. Those who
failed to connect were assigned the maximum time of 40:08.
}
\label{table:selfreported-tech}
\end{table}

@@

\begin{table*}[h]
\centering
\begin{tabular}{l r r r r r}
& \multicolumn{1}{r}{} & \multicolumn{1}{r}{Less than once} & \multicolumn{1}{r}{A few times}& \multicolumn{1}{r}{Several times}& \multicolumn{1}{r}{}\\
& \multicolumn{1}{r}{Never} & \multicolumn{1}{r}{a month} & \multicolumn{1}{r}{a month}& \multicolumn{1}{r}{a week}& \multicolumn{1}{r}{Daily}\\
\noalign{\hrule}
HTTPS on web pages& 00/00 & 00/00 & 00/00 & 00/00 & 00/00 \\
Proxies or censorship circumvention tools & 00/00 & 00/00 & 00/00 & 00/00 & 00/00 \\
Virtual private networks (VPNs) & 00/00 & 00/00 & 00/00 & 00/00 & 00/00 \\
File or disk encryption & 00/00 & 00/00 & 00/00 & 00/00 & 00/00 \\
Anonymity systems (e.g. Tor) & 00/00 & 00/00 & 00/00 & 00/00 & 00/00 \\
Email encryption (e.g. PGP) & 00/00 & 00/00 & 00/00 & 00/00 & 00/00 \\
Instant messaging encryption & 00/00 & 00/00 & 00/00 & 00/00 & 00/00 \\
Voice communication encryption & 00/00 & 00/00 & 00/00 & 00/00 & 00/00 \\
\end{tabular}
\caption{
An overview of the results of the experiment. Those who
failed to connect were assigned the maximum time of 40:08.
}
\label{table:selfreported-software}
\end{table*}

>>>>

Bridges are unlisted Tor relays that serve as an alternative entry node.
Bridges can be unlisted relays that behave similarly to a reular Tor relay,  
but most run a pluggable tranport (referred to as ``transport'' for shorthand) that obfuscates traffic. 
Most transports rely on the secrecy of their static IP addresses for their effectiveness.
These include ``fte'' and ``fte-ipv6''~\cite{fte},
which disguise the Tor protocol as another protocol (such as HTTP), and
``obfs3''~\cite{obfs3}, ``obfs4''~\cite{obfs4}, and ``scramblesuit''~\cite{scramblesuit},
which encrypt or alter the Tor protocol to appear as random noise.
Other transports route traffic through other services and do not need secret IP address. 
``flashproxy''~\cite{flashproxy} connects through third party web browsers,
and the ``meek''~\cite{fifield2015blocking} options route traffic
through content delivery networks. Fig.~\ref{fig:bridge-options} shows the bridge and transport options at the time of the study.

@@

\subsection{State and Corporate Censorship}
State level censors block access to the Tor network by blocking Tor relays, which are publicly listed. Some also employ more sophisticated techniques such as deep packet inspection and protocol detection. This means that users can connect to the Internet, but not through Tor. The thoroughness of cenrsorship is what requries different bridges and transports.

A local proxy is required to connect in certain managed networks (i.e. company and university firewalls). This usually means that users cannot connect to the Internet at all without a proxy, including conencting to the Internet through Tor. The user must be able to connect to the Internet through thier proxy before trying to connect to the Internet with Tor.

@@

\subsection{Testing Pipeline} 
Two researchers first performed a cognitive walkthough~\cite{cognitive-walkthrough} to prepare for user testing. A cognitive walkthough is evaluation method that requires usability evaluators to work through a series of tasks from the perspective of the user, usually to understand a system's learnability for new or infrequent users.

@@

We concluded with a summative usability test~\cite{summative} that measured the usability of the current and redesigned interface. This testing is a usually used as quality assurance tool to test features. In short, formative testing tells you {\it what} is is not usable, while summative testing testing tells you {\it if} it is or is not usable. Twenty users is considered to be a minimum for statistically significant measurments~\cite{howmanyusers}, so we recruited twenty participants for each experimental condition.

@@

\begin{itemize}
\item {\bfseries Completion rate:}  percentage of users that connect to Tor in an experimental condition. 
\item {\bfseries Connection time:} time from Tor Browser startup to a succcessful connection to Tor. 
\item {\bfseries Configuration time:} time users spent in Tor Launcher configuring bridges and proxies.
\end{itemize}

@@

We simulated three environments of increasing severity in censorship (E1, E2, E3).
Table~\ref{tab:environments} summarizes them and explains what is required to connect to Tor. We chose to 
simulate environments for the stability and reproducibility of the 
experiment, as real censored networks are voilatile and complex.

@@

\subsection{Procedure} 
Two researchers performed the cognitive walkthough on the Tor Browser 5.0.3 Tor Launcher GUI, the most recent version deployed at the time (Figure~\ref{fig:old-interface}). We systematically tried action sequences from the perspective of a typical user, which we defined as a first time or infrequent user with almost no previous knowledge about network components involved in connecting to Tor.

@@

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{tor-digraph.png}
\caption{
A digraph illustrating the potential user paths through the interface. Non-leaf nodes are screens in the user interface (start, bridge 1, bridge 2, proxy 1, proxy 2, and progress). Leaf nodes are various end states (quit, success, or error). Tansitions between these nodes denote user actions. For details of each end state, see Appendix ~\ref{states}. 
}
\label{fig:digraph}
\end{figure*}

@@

\subsection{Recruitment}
We recruited people from Craigslist using the recruitment text in Appendix~\ref{qualitative-recruitment}, which linked an presecreening survey that collected demographics (Appendix~\ref{qualitative-prescreening}). We pre-screened~\cite{screening} for diversity in gender, age, technical expertise, use of security tools, and familiarity with Tor in a small participant pool. Of our 16 recruited participants, 50\% were male. Ages ranged from 20 to~62 years ($\mu = 30.5$, $\sigma = 13.5$). One participant declined to submit their age, so the previous calcuations were done without thier information. 100\% had at least some college education. We took participants' self-reported familiarity with technical terms use of security tools with skepticism (Appendix~\ref{prescreening-responses}). We verified their self-reported familiarity with Tor Browser in-person, and found that 4 used it, 5 heard of it but not used it, and the remaining 8 never heard of or used it. The main objective of this question was to identify new users versus infrequent users. We considered participants who had never heard of Tor or have only heard of Tor to be new users and those who have used Tor to be previous users.

% gender: Male: 8/Female: 8
% education: At least some college 16
% ages: 22, 23, 34, 52, 25, 22, 29, 21, 25, didn't answer, 20, 20, 26, 24, 62, 52

@@

After participants completed the browsing tasks (or ran out of time),
we asked them standard interview questions about their experience (Appendix~\ref{interview-questions}) and took notes of their responses. We then followed up with participant-specific questions to verify any hypotgit heses we had from observation (e.g. ``the participant was selecting bridges at random''). We paid each participant~\$30 for their time.

\subsection{Results} 
We give a summary of what our participants did below. We watched the screen recording to summerize their actions and referred to their interviews for insight into why they took specific actions.

@@

In E2, a bridge was required to connect, but any bridge worked. Configuring a proxy was optional.
Participants in E2 {\it eventually} connected using the recommended bridge, but spent a fair bit of time waiting for direct connections to fail and unsucccessfully configuring proxies. 
Observations in E2:

@@

\subsection{Procedure} 
Three researchers agreed on security and usability design principles. 
We then rewatched screen capture videos and read interview transcirptions to brainstorm design changes. We provided the security and usability design principles, screen capture videos, interview transcriptions, and our suggested changes to a user interface designer, who iteratively redesigned the interface with our feedback and user interface best practices in mind. Figure~\ref{fig:new-interface} shows our redesign of the interface.

\begin{figure*}
\centering
\begin{subfigure}[b]{0.35\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-first.png}
	\caption{The first screen. We reduced the text on the screen and clarified that configuration is for heavily censored enviroinments.}
	\label{fig:new-first}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.35\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-proxyYES.png}
	\caption{The interface detects the need for a proxy. Proxy fields (same as ones in Figure \ref{fig:old-proxy-yes} are hidden until you click``configure.''}
	\label{fig:new-proxy}
\end{subfigure}
\begin{subfigure}[b]{0.35\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeSettings.png}
	\caption{There is only one bridge screen now. The default is to connect without one.}
	\label{fig:new-nobridge}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.35\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeSettings-default.png}
	\caption{We give short instructions on when to use a bridge. Users can configure one here.}
	\label{fig:new-bridge}
\end{subfigure}
\begin{subfigure}[b]{0.35\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeSettings-combobox.png}
	\caption{The transports selections are the same.}
	\label{fig:new-bridge-combobox}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.35\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeHelp.png}
	\caption{These instuctions are also the same.}
	\label{fig:new-bridge-help}
\end{subfigure}
\begin{subfigure}[b]{0.35\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-summary.png}
	\caption{This screen summarized how they would connect to Tor. There is more information if bridges and proxies are configured.}
	\label{fig:new-summary}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.35\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-progress.png}
	\caption{A checkpoint progress bar with connection information. There are more checkpoints if bridges and proxies are configured.}
	\label{fig:new-progress}
\end{subfigure}
\caption{
A redesigned version of the Tor Browser 5.0.3. Tor Launcher GUI. Screens are in the order that they appear. 
}
\label{fig:new-interface}
\end{figure*}

\subsection{Design Princples} 
The interface currently favors a guided manual configuration over an automated configuration with network probing. Our redesign preserves this approach and has no user-dependent inputs, no network-dependent inputs, and minimal information leaks.

@@

\subsection{Recruitment}
We recruited  people using the recruitment text in Appendix~\ref{quantitative-recruitment}. We recruited 65 participants from Craiglist and 59 participants from the <redacted lab> participant pool. <Redacted lab> encouraged the use of their participant pool, but we bargained to recruit participants from Craigslist to ensure a diverse set of participants. Although the <redacted lab>'s participant pool is not limited to students and staff from <redacted institution>, it was estimated that a large majority were.

{\color {red} Of our recruited 124 participants, 56.8\% were male. Ages ranged from 18 to~68 years ($\mu = 28.9$, $\sigma = 12$). 56.8\% were male. 84.8\% of our participants had a college education.} We distributed participants evenly across experimental condition, about 20 in each interface and environment combination. Although there is variation in gender and age in each experimental condition, we ensured each condition had about half Craiglist recruited participants and half <redacted lab>  pool participants.

@@

\subsection{Procedure}
Participants were assigned to a computer at random, which effectively assigned them to a simulated censorship environment combination at random. Before the experiment began, participants were verbally informed of the purpose of the study, what data was collected, and any associated risks. If they wished to participate, they were ifnormed again in writing and consented by signing the document. To be thorough, we clarified that they could stop at any time during the experiment with no negative consequences.

The experiment formally began by informing participants of the simulated censorship environment, giving them their worksheet, and informing them that Tor browser is necessary to circumvnt censorship (Appendix~\ref{quantitative-script}). This time, the worksheet only asks users to visit one blocked website (Wikipedia) and explicitly reminds users to use Tor to do so. Before participants started their tasks, we reminded them that their screens are being recorded so they should not log into anything that shows personal information. We gave users a chance to ask any questions about the experiment or task.

@@

%table
\begin{table}[t]
\centering
\input{attempts-bridge-proxy.tex}
\caption{
Network components that led to the first successful bootstrap
in each condition.
Most successful E1 participants used a direct connection,
but a few optionally used an obfs3 bridge.
All successful E2 participants used 
an obfs3 bridge (the recommended option)---none used 
flashproxy, fte, fte-ipv6, obf4, or scramblesuit bridges to connect. 
Most successful E3 participants
used a meek bridges, disfavoring meek-azure.
One E3 participant succeeded in an unexpected way
by using an open proxy and configuring it to bypass our 
simulated environment.
}
\label{tab:attempts-bridge-proxy}
\end{table}

@@

% failure observations
17\% (19 of 114) of participants were not able to successfully connect to Tor. Five (P73, P75, P89, P91, P106, P110) tried a direct connection. When that failed, they assumed there was something wrong with their computer, network settings, or the Tor network and never tried to configure bridges or proxies. Five (P74, P92, P105, P107, P113) users who need a bridge assumed that they needed a proxy to connect to Tor. We belive this may be due to the fact that the OLD interface defaults to showing users the proxy page (because it is the one before the progress screen) when a connection fails. Five (P90, P93, P108, P111, P114) users who needed a meek or custom bridge tried the suggested bridge (obfs3), but didn't know what to do when that failed. Two (P94, P109) users who needed a meek or custom bridge tried to get custom bridges but failed to format their email content correctly to get a response from the bridges autoresponder. We suspect that they would have succeeded if they had gotten a response.

@@

\subsubsection{Connection time} 
Connection time is the time from Tor Browser starup to the first successful Tor bootstrap. Non-finishing participants are assigned the maximum experiment time of 40:08. Table~\ref{table:participant-summary} summarizes the median times while Figure~\ref{fig:time_to_success_clamped} shows their distribution. Figure~\ref{fig:time_to_success_ecdf} shows the cumulative success rates over time.

@@

\subsubsection{Configuration Time} 
Configuration time is the time spent configuring network components, which we define as the completion time minus any time spent on the progress screen. Table~\ref{table:participant-summary} shows the median times and Figure~\ref{fig:time_to_success_active_clamped} shows their distribution. Table~\ref{table:median_time} shows the percentage of time spent on each screen. Note that the time spent configuring bridges and proxies is {\it not} equivalent to the amount of time participants spent trying to connect, which would be the connection time minus the time spent on the progress screen for the last time (time Tor takes to bootstrap after a valild configuration).

%things to keep in mind
We believe that configuration time is a meaningful metric because 1) bootstrapping can take a couple minutes, which dominates measurements for users do not need much time to configure their connection, such as participants in E1. and 2) some mistakes, such as using a syntactically valid but unsuable proxy, generate non-interruping warnings and let the users wait indefinitely at until they manually cancel the connection to try again. But this is not the most accurate measurement of time spent configuring, since it does not reflect how some participants searched for help in another browser while waiting on the progress screen.

@@

\subsection{Usability of Tor Launcher} 
In total, 63\% (72 of 114) of first attempts to connect failed and 79\% (363 of 458) of total attempts to connect failed. 
On average, users who required a bridge took over 3 minutes to connect to Tor, and users who required a meek or cutsom bridge took over 20 minutes.

@@

Participants in a laboratory setting may alter their due to their awareness of being observed~\cite{mccarney2007hawthorne}. We are aware that our participants were likely motivated differently compared to real users. We believe that participants were likely overmotivated to connect to Tor because they were being observed and recieving a monetary reward. If true, this makes our results are a conservative estimate of the current usability problems.

@@

We only tested interface on Windows machines, which were the machines available at <redacted>. %Xlab.
The configuration interface leverages the native operating system's styling and elements, making the configuration interface on Windows look slightly different from the OSx or Linux equivalent. Additionally, we acknowledge that participants' unfamilarity with Windows may have affected our experiment, but we believe that this affected all experimental conditions minorly and equally.

@@

\section {Acknowledgments}
Many generous people helped us along the way. <Redacted> assisted with testing our setup and teardown scripts, offered recruitment services, and allowed us to run experiments after <redacted lab>'s hours. <Redacted> and <redacted> were instrumental during the design process, as they helped me interate through many not-so-great ideas.  <Redacted>,and <redacted> provided me with insider insight into the design decisions made at Tor.
% Rowilma del Castillo. Nima Fatemi and Isabela Bagueros.  Georg Koppen and the Tor UX team.

@@

{\color {red}
\section{Prescreening Survey Responses}
\label{prescreening-responses}
We asked people how familiar they were with some technical terms and security tools during our prescreening survey for formative usability testing. We show the responses from the particpants that we chose.

\begin{table}[h]
\centering
\begin{tabular}{l r r}
& Familiarity\\
\noalign{\hrule}
Malware & 81\% (13/16) \\ %13/16
Proxy services & 69\% (11/16)\\ %11/16
Phishing & 63\% (10/16)\\ %10/16
SSL & 63\% (10/16)\\%10/16
X.511 certificates & 25\% (4/16)\\ %4/16
Tor & 50\% (8/16)\\ %8/16
\end{tabular}
\caption{
An overview of the results of the experiment. Those who
failed to connect were assigned the maximum time of 40:08.
}
\label{table:selfreported-tech}
\end{table}

@@

\begin{table*}[h]
\centering
\begin{tabular}{l r r r r r r}
& \multicolumn{1}{r}{} & \multicolumn{1}{r}{Less than once} & \multicolumn{1}{r}{A few times}& \multicolumn{1}{r}{Several times}& \multicolumn{1}{r}{} & \multicolumn{1}{r}{Missing}\\
& \multicolumn{1}{r}{Never} & \multicolumn{1}{r}{a month} & \multicolumn{1}{r}{a month}& \multicolumn{1}{r}{a week}& \multicolumn{1}{r}{Daily} & \multicolumn{1}{r}{answer}\\
\noalign{\hrule}
HTTPS on web pages				& 13\% (2/16) & 0\% (0/16) & 1\% (1/16) & 25\% (4/16) & 56\% (9/16) & 0\% (0/16) \\
Proxies or censorship circumvention tools & 50\% (8/16) & 13\% (2/16) & 13\% (2/16) & 1\% (1/16) & 1\% (1/16) & 13\% (2/16) \\
Virtual private networks (VPNs) 		& 44\% (7/16) & 31\% (5/16) & 13\% (2/16) & 0\% (0/16) & 1\% (1/16) & 1\% (1/16) \\
File or disk encryption 				& 50\% (8/16) & 1\% (1/16) & 13\% (2/16) & 0\% (0/16) & 25\% (4/16) & 1\% (1/16) \\
Anonymity systems (e.g. Tor) 			& 63\% (10/16) & 13\% (2/16) & 1\% (1/16) & 13\% (2/16) & 0\% (0/16) & 1\% (1/16) \\
Email encryption (e.g. PGP) 			& 50\% (8/16) & 19\% (3/16) & 19\% (3/16) & 0\% (0/16) & 1\% (1/16) & 1\% (1/16) \\
Instant messaging encryption 			& 44\% (7/16) & 25\% (4/16) & 13\% (2/16) & 1\% (1/16) & 1\% (1/16) & 1\% (1/16) \\
Voice communication encryption 		& 81\% (13/16) & 1\% (1/16) & 1\% (1/16) & 0\% (0/16) & 0\% (0/16) &1\% (1/16)\\
\end{tabular}
\caption{
An overview of the results of the experiment. Those who
failed to connect were assigned the maximum time of 40:08.
}
\label{table:selfreported-software}
\end{table*}
